### 2016-05-19 2016-lrec-tyvmorph/poster.tex
and a good first draft of the final version?
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68639 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.6}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

@@

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\fontsize{5.75pt}{5.75pt}\selectfont}
\renewcommand*{\intitlepunct}{\space}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.2]%, auto]

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -1in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp-2}
		%\begin{itemize}
		%\end{itemize}
		\vspace{1.55in}
		\dividerspace{}

@@

				%\item Current annotation of a dependency treebank for Kazakh:\\
				%a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%%\item Leading to
				%\begin{itemize}
				%	\item Improved rule-based morphological disambiguation% (constraint grammar)
				%	\item Improved morphological analyser %for Kazakh
				%	\item A syntactic dependency treebank %for Kazakh
				%\end{itemize}
				%%\item Work on rule-based morphological disambiguation with constraint grammar
			%\end{itemize}
			\htwo{Future work}
				\begin{itemize}
					%\item Annotate more gold standard text in more Turkic languages
					%\item Research cross-linguistic techniques for analysing Turkic
					\item Dependency parsing (native and crosslingual)
					\item Increase number of stems
					\item Make more available to linguists
					\item Integrate into end-user applications (spellchecking, MT)
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
				\includegraphics[width=\textwidth]{img/tyv-spelling}
		}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.6}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}
\usepackage{tikz-dependency}

@@

\newcommand{\tyv}[1]{\textit{#1}}
\newcommand{\tgloss}[1]{\tyv{#1}}
\newfontfamily\udfont[Scale=1.3,Letters=SmallCaps]{Linux Libertine O}
\newcommand{\udtag}[1]{{\ll \textsc{#1}}}
\newcommand{\udlabel}[1]{{\udfont #1}}

@@

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\fontsize{5.735pt}{5.735pt}\selectfont}
\renewcommand*{\intitlepunct}{\space}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.212]%, auto]

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -2.25in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\resizebox{\textwidth}{!}{
        \begin{dependency}[theme = simple, font = \small]
           \begin{deptext}[column sep=0.08cm]
%               1         2         3          4              5          6          7        8
                %Мен \& тыва \& хүреш \& -биле \& сургуул \& кылбастай \& бээримге \& ачам \& хомудаан \& . \\
                Бис \& кожууннуң \& соңгукчулары \& -биле \& ажылды \& чорутпастай \& бээривиске, \& көргүзүглер \& баксыраан \& . \\
%                \gmk{prn} \& \gmk{n.attr} \& \gmk{n.nom} \& \gmk{post} \& \gmk{n} \& \gmk{v.tv.prc} \& \gmk{vaux} \& \gmk{n.px1sg.nom}  \& \gmk{v.iv.past} \&  \\
                \gmk{prn} \& \gmk{n.gen} \& \gmk{n.pl.px3sp} \& \gmk{post} \& \gmk{n.acc} \& \gmk{v.tv.prc} \& \gmk{vaux} \& \gmk{n.pl.nom}  \& \gmk{v.iv.past} \&  \\
                \tgloss{We} \& \tgloss{district} \& \tgloss{constituents} \& \tgloss{with} \& \tgloss{business} \& \tgloss{having stopped conducting} \& \tgloss{} \& \tgloss{figures} \& \tgloss{worsened} \& \\
                \end{deptext}
                \depedge{6}{1}{\udlabel{nsubj}}
                \depedge{3}{2}{\udlabel{nmod:poss}}
                \depedge{3}{4}{\udlabel{case}}
                \depedge{6}{3}{\udlabel{nmod}}
                \depedge{6}{5}{\udlabel{dobj}}
                \depedge{6}{7}{\udlabel{aux}}
                \depedge{9}{8}{\udlabel{nsubj}}
                \depedge{9}{6}{\udlabel{advcl}}
                \depedge{9}{10}{\udlabel{sent}}
                \deproot[edge unit distance=3ex]{9}{\udlabel{root}}
        \end{dependency}}\\
		\setlength\fboxsep{0.5em}
		\setlength\fboxrule{0pt}
		\fbox{\includegraphics[width=0.63\textwidth]{img/korp-2}}
		%\begin{itemize}
		%\end{itemize}
		\vspace{1.8625in}

		\dividerspace{}

@@

				%\item Current annotation of a dependency treebank for Kazakh:\\
				%a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%%\item Leading to
				%\begin{itemize}
				%	\item Improved rule-based morphological disambiguation% (constraint grammar)
				%	\item Improved morphological analyser %for Kazakh
				%	\item A syntactic dependency treebank %for Kazakh
				%\end{itemize}
				%%\item Work on rule-based morphological disambiguation with constraint grammar
			%\end{itemize}
			\htwo{Future work}
				\begin{itemize}
					%\item Annotate more gold standard text in more Turkic languages
					%\item Research cross-linguistic techniques for analysing Turkic
					\item Dependency parsing (native and crosslingual)
					\item Increase number of stems
					\item Make more available to linguists
					\item Integrate into end-user applications (spellchecking, MT)
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
				\vspace{0.3em}
				\includegraphics[width=\textwidth]{img/tyv-spelling-cropped}
				\vspace{-0.1in}
		}
